### 2017-02-02 local-capability-machine.tex
Prove another of the FTLR lemmas and fix a bug in the semantics: subseg should not be allowed for enter caps.
bib, proof

                                                \text{if $\memreg(r) = \stdcap[\permp]$} \\

@@

                                                \quad\text{and $c = (\permp,n_1,n_2,\addr)$}

@@

\begin{proof}[Proof of Theorem~\ref{thm:world-existence}]
  The theorem follows from a more general solution theorem for the
  category of $P$ preordered cofe's~\cite{bizjak-note}. 
  We define two functors $F_1$ and $F_2$ from $P^{op}\times P^{op}$ to
  $P$. 
  \begin{align*}
     F_1((X,{\futurestr}'),(Y,{\futurewk}')) = \\
     (\blater (\nats \finparfun ( & \{\revoked\}  + \\
                                          & \{\temp\} \times \States \times \Rels \times (\States \fun ((Y,{\futurewk}') \monnefun \UPred{\HeapSegments})) + \\
                                          & \{\perma\} \times \States
                                            \times \Rels \times
                                            (\States \fun ((X,{\futurestr}')
                                            \monnefun
                                            \UPred{\HeapSegments})))),
                                        \futurestr)
  \end{align*}
  and
  \begin{align*}
     F_2((X,{\futurestr}'),(Y,{\futurewk}')) = \\
     (\blater (\nats \finparfun ( & \{\revoked\}  + \\
                                          & \{\temp\} \times \States \times \Rels \times (\States \fun ((Y,{\futurewk}') \monnefun \UPred{\HeapSegments})) + \\
                                          & \{\perma\} \times \States
                                            \times \Rels \times
                                            (\States \fun ((X,{\futurestr}')
                                            \monnefun
                                            \UPred{\HeapSegments})))),
                                        \futurestr)
  \end{align*}
  The orderings $\futurestr$ and $\futurewk$ used in the definition of
  $F_1$ and $F_2$ are defined by the properties given above.
  Note that the image of $F_1$ and $F_2$ only differ in the ordering
  relation, i.e., letting $U$ denote the forgetful functor from the
  category of preordered cofe's to the category of cofe's, we have
  $U \circ F_1 = U \circ F_2$.
  From~\cite{bizjak-note} it then follows that there exists a cofe $\Wor$ and two
  preorderings $\futurestr$ and $\futurewk$ and an isomorphism $\xi$ satisfying the properties
  claimed in theorem.
  (Here, in the proof, we have written the ordering explicitly on the cofe when
  using monotone non-expansive functions; in the theorem formulation
  we have instead annotated the arrow to indicate which ordering is used.)
\end{proof}

@@

 \begin{lemma}[Conditions for subseg instruction are sufficient]
   \label{lem:conds-subseg-suffice}
   If
   \begin{itemize}
   \item $\npair{((\perm',\gl'),\start',\addrend',\addr')} \in \stdvr(W)$
   \item $\start' \leq \start''$
   \item $\addrend'' \leq \addrend'$
   \end{itemize}

   then $\npair{((\perm',\gl'),\start'',\addrend'',\addr')} \in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   TODO
 \end{proof}

@@

      ((\perm',\gl'),\start'',\addrend'',\addr')$

@@

        ((\perm',\gl'),\start'',\addrend'',\addr')$: \\

>>>>

                                                \text{if $\memreg(r) = \stdcap$} \\

@@

                                                \quad\text{and $c = ((\perm,\gl),n_1,n_2,\addr)$}

@@

\begin{proof}[Proof of Theorem~\ref{thm:world-existence}]
  The theorem follows from a more general solution theorem for the
  category of $P$ preordered \cofes, see~\cite{bizjak-note}. 
  We define two functors $F_1$ and $F_2$ from $P^{op}\times P^{op}$ to
  $P$. 
  \begin{align*}
     F_1((X,{\futurestr}'),(Y,{\futurewk}')) = \\
     (\blater (\nats \finparfun ( & \{\revoked\}  + \\
                                          & \{\temp\} \times \States \times \Rels \times (\States \fun ((Y,{\futurewk}') \monnefun \UPred{\HeapSegments})) + \\
                                          & \{\perma\} \times \States
                                            \times \Rels \times
                                            (\States \fun ((X,{\futurestr}')
                                            \monnefun
                                            \UPred{\HeapSegments})))),
                                        \futurestr)
  \end{align*}
  and
  \begin{align*}
     F_2((X,{\futurestr}'),(Y,{\futurewk}')) = \\
     (\blater (\nats \finparfun ( & \{\revoked\}  + \\
                                          & \{\temp\} \times \States \times \Rels \times (\States \fun ((Y,{\futurewk}') \monnefun \UPred{\HeapSegments})) + \\
                                          & \{\perma\} \times \States
                                            \times \Rels \times
                                            (\States \fun ((X,{\futurestr}')
                                            \monnefun
                                            \UPred{\HeapSegments})))),
                                        \futurestr)
  \end{align*}
  The orderings $\futurestr$ and $\futurewk$ used in the definition of
  $F_1$ and $F_2$ are defined by the properties given above.
  Note that the image of $F_1$ and $F_2$ only differ in the ordering
  relation, i.e., letting $U$ denote the forgetful functor from the
  category of preordered \cofes\ to the category of \cofes, we have
  $U \circ F_1 = U \circ F_2$.
  From~\cite{bizjak-note} it then follows that there exists a \cofe\ $\Wor$ and two
  preorderings $\futurestr$ and $\futurewk$ and an isomorphism $\xi$ satisfying the properties
  claimed in theorem.
  (Here, in the proof, we have written the ordering explicitly on the \cofe\ when
  using monotone non-expansive functions; in the theorem formulation
  we have instead annotated the arrow to indicate which ordering is used.)
\end{proof}

@@

 \begin{lemma}[Conditions for subseg instruction are sufficient]
   \label{lem:conds-subseg-suffice}
   If
   \begin{itemize}
   \item $\npair{((\perm,\gl),\start,\addrend,\addr)} \in \stdvr(W)$
   \item $\start \leq \start'$
   \item $\addrend' \leq \addrend$
   \item $\perm \neq \entry$
   \end{itemize}

   then $\npair{((\perm,\gl),\start',\addrend',\addr)} \in \stdvr(W)$
 \end{lemma}
 \begin{proof}
   Follows easily from the definitions of $\stdvr(W)$, $\readCond{}$,
   $\writeCond{}$, $\execCond{}$.
 \end{proof}

@@

      ((\perm',\gl'),\start'',\addrend'',\addr')$ and $\perm' \neq \entry$

@@

        ((\perm',\gl'),\start'',\addrend'',\addr')$ and $\perm' \neq \entry$: \\
